Ants-Review: an Ethereum-Based Protocol for Peer Reviews

### 2020-11-15 article.tex
quick recap

\title{Ants-Review: a Protocol for Open Anonymous Peer Reviews}

@@

\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}

@@

\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France

@@

\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Blockchain Engineer, London, UK \\

@@

\keywords{Blockchain \and Ethereum \and Peer-review \and Incentivization.}

@@

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
\label{fig:contracts}
\end{figure}

>>>>

\title{Ants-Review: an Ethereum-Based Protocol for Peer Reviews}

@@

\author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}

@@

\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France

@@

\and Smart Contract Engineer, London, United Kingdom \\

@@

\keywords{Blockchain \and Ethereum \and Peer-review \and Incentivization}

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
\label{fig:contracts}
\end{figure}
